---
title: "Peer Assignment 1"
author: "Toni Massó"
date: "10/05/2015"
output:
  html_document:
    keep_md: yes
    pandoc_args:
    - +RTS
    - -K64m
    - -RTS
---


```{r}
library(dplyr)
library(ggplot2)
library(scales)
```
###Loading and preprocessing the data

```{r}

data1<-read.csv('data/activity.csv')
data1$interval <- sapply(data1$interval,FUN=function (i) {  sprintf("%02d:%02d", i %/% 100, i %% 100)})
data1$date2<-paste(data1$date,data1$interval)
data1$date2<-as.POSIXlt(data1$date2,'%Y-%m-%d %H:%M')
data0<-data1
```

###What is mean total number of steps taken per day?

```{r MeanTotalSteps}
data1<- na.omit(data1)
data2<-aggregate(data1$steps,by=list(Date=data1$date),FUN=sum)
colnames(data2)<- c('Date', 'SumStepsPerDay')
hist(data2$SumStepsPerDay,breaks=seq(0,25000,by=1000))
```

####Mean per day:
```{r}
dataMean<-aggregate(data1$steps,by=list(Date=data1$date),FUN=mean)
dataMean
```

####Median per day:
```{r}
dataMedian<-aggregate(data1$steps,by=list(Date=data1$date),FUN=median)
dataMedian
```

###What is the average daily activity pattern?
```{r}
data3<-aggregate(data1$steps,by=list(Interval=data1$interval),FUN=mean,na.rm=TRUE)
colnames(data3)<- c('Interval','MeanStepsInterval')
data3$Interval<-strptime(data3$Interval,format='%H:%M')
ggplot( data = data3, aes(Interval,MeanStepsInterval)) + geom_line() + scale_x_datetime( breaks=("120 min"),labels=date_format("%H:%M"))
```

####Max Interval 
```{r}
data3[data3$MeanStepsInterval== max(data3$MeanStepsInterval),]
```

###Imputing Missing Values
```{r}
sumNASteps<-sum(is.na(data0$steps))
sumNADate<-sum(is.na(data0$date))
sumNAInterval<-sum(is.na(data0$interval))
```
####NAs in Steps field
```{r}
sumNASteps
```
####NAs in Date field
```{r}
sumNADate
```
####NAs in Interval field
```{r}
sumNAInterval
```
####Filling NA values

I fill NA values with Median value of the interval.

```{r}
data4<-data1
for(i in 1:length(data4$steps)){
        if(is.na(data4$steps[i])){
                data4$steps[i]<-data3$MeanStepsInterval[substring(as.character(data3$Interval),12,16)==data4$interval[i]]
        }
}
data5<-aggregate(data4$steps,by=list(Date=data4$date),FUN=sum)
colnames(data5)<- c('Date', 'SumStepsPerDay')
hist(data5$SumStepsPerDay,breaks=seq(0,25000,by=1000))

```

####Mean per day withou NA:
```{r}
dataMean<-aggregate(data4$steps,by=list(Date=data4$date),FUN=mean)
dataMean
```

####Median per day withou NA:
```{r}
dataMedian<-aggregate(data4$steps,by=list(Date=data4$date),FUN=median)
dataMedian
```
###Are there differences in activity patterns between weekdays and weekends?:
```{r}
Sys.setlocale("LC_TIME", "en_US.UTF-8")
data1$weekday<-weekdays(data1$date2)
dataWeek<-aggregate(data1$steps,by=list(Weekday=data1$weekday,Intervals=data1$interval),FUN=mean,na.rm=TRUE)
dataWeek$Intervals<-strptime(dataWeek$Intervals,format='%H:%M')
ggplot( data = dataWeek, aes(Intervals,x)) + geom_line() + scale_x_datetime( breaks=("120 min"),labels=date_format("%H:%M"))
dataWeek$day<-'Weekday'
dataWeek[dataWeek$Weekday=='Saturday'| dataWeek$Weekday=='Sunday','day']<-'Weekend'
p<-ggplot( data = dataWeek, aes(Intervals,x)) + geom_line() + scale_x_datetime( breaks=("120 min"),labels=date_format("%H:%M")) + scale_y_continuous(name="Number of Steps")
p + facet_grid(day ~ .)
```





